### 2009-12-07 doc/manuals/user_interface/ui-job.tex
Added arcinfo, notes on OR in arcstat/arccat/arcget etc, some more translations

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

\begin{framed}
  When several of the \verb#-a#,  \verb#-j#, \verb#-c#, \verb#-s# and \verb#[job...]#
  command line options are specified, the comand returns information for \textbf{ALL} jobs that
  match either of the criteria (logical OR).

  For example, \verb#arcstat -s Finished -c mycluster <jobid># will return information about all finished
  jobs on the Grid, plus about all jobs (in any state) on the cluster \verb#mycluster#, plus about the job \verb#<jobid>#.
\end{framed}

@@

\begin{framed}
  When several of the \verb#-a#,  \verb#-j#, \verb#-c#, \verb#-s# and \verb#[job...]#
  command line options are specified, the comand prints logs for \textbf{ALL} jobs that
  match either of the criteria (logical OR).

  For example, \verb#arccat -s Finished -c mycluster <jobid># will print logs of all finished
  jobs on the Grid, plus of all jobs (in any state) on the cluster \verb#mycluster#, plus of the job \verb#<jobid>#.
\end{framed}

@@

\begin{framed}
  When several of the \verb#-a#,  \verb#-j#, \verb#-c#, \verb#-s# and \verb#[job...]#
  command line options are specified, the comand retrieves \textbf{ALL} jobs that
  match either of the criteria (logical OR).

  For example, \verb#arcget -s Finished -c mycluster <jobid># will retrieve all finished
  jobs on the Grid, plus all jobs (in any state) on the cluster \verb#mycluster#, plus the job \verb#<jobid>#.
\end{framed}

@@

\subsection{arcinfo}
\label{sec:arcinfo}

The \texttt{arcinfo} \index{arcinfo}\index{commands:arcinfo} command is used to obtain status information about clusters on the Grid.

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcinfo [options]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-c, --cluster}&\verb#[-]#\textit{name}&explicitly select or reject a specific site\\
   \texttt{-i, --index}&\textit{url}&explicitly select or reject (-) a specific index server\\
   \texttt{-l, --long}& & long format (extended information)\\
   \texttt{-t, --timeout}&\textit{seconds}&timeout in seconds (default 20)\\
   \texttt{-d, --debug}&\textit{debuglevel}&debug level, FATAL, ERROR, WARNING, INFO, VERBOSE or DEBUG - default WARNING\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}&&print version information\\
   \texttt{-h, --help}&&print help page\\
\end{longtable}

The  \texttt{arcinfo}  command is used to obtain information about clusters and queues (\textit{targets})
available on the Grid. Either the \verb#--cluster# or \verb#--index# flag should be used to specify the
target(s) which should be queried for information. Both of these flags take a service endpoint as argument.
See \texttt{arcsub} and the configuration notes in Section~\ref{sec:client.conf} for description of these.

Detailed information about queried computing services can be obtained by specifying the \verb#--long# flag.

When  specifying  the  \verb#--index#  flag,  the  information about the computing services registered at the index server will
be queried, rather than the status of the index server itself.

@@

\begin{framed}
  When several of the \verb#-a#,  \verb#-j#, \verb#-c#, \verb#-s# and \verb#[job...]#
  command line options are specified, the comand kills \textbf{ALL} jobs that
  match either of the criteria (logical OR).

  For example, \verb#arckill -s INLRMS:R -c mycluster <jobid># will kill all running
  jobs on the Grid, plus all jobs (in any state) on the cluster \verb#mycluster#, plus the job \verb#<jobid>#.
\end{framed}

@@

\begin{framed}
  When several of the \verb#-a#,  \verb#-j#, \verb#-c#, \verb#-s# and \verb#[job...]#
  command line options are specified, the comand cleans \textbf{ALL} jobs that
  match either of the criteria (logical OR).

  For example, \verb#arcclean -s FAILED -c mycluster <jobid># will clean all failed
  jobs on the Grid, plus all jobs (in any state) on the cluster \verb#mycluster#, plus the job \verb#<jobid>#.
\end{framed}

@@

\begin{framed}
  When several of the \verb#-a#,  \verb#-j#, \verb#-c#, \verb#-s# and \verb#[job...]#
  command line options are specified, the comand renews proxies for \textbf{ALL} jobs that
  match either of the criteria (logical OR).

  For example, \verb#arcrenew -s FAILED -c mycluster <jobid># will renew proxies of all failed
  jobs on the Grid, plus of all jobs (in any state) on the cluster \verb#mycluster#, plus of the job \verb#<jobid>#.
\end{framed}

@@

\begin{framed}
  When several of the \verb#-a#,  \verb#-j#, \verb#-c#, \verb#-s# and \verb#[job...]#
  command line options are specified, the comand resumes \textbf{ALL} jobs that
  match either of the criteria (logical OR).

  For example, \verb#arcresume -s FAILED -c mycluster <jobid># will resume all failed
  jobs on the Grid, plus all jobs (in any state) on the cluster \verb#mycluster#, plus the job \verb#<jobid>#.
\end{framed}

@@

\begin{framed}
  When several of the \verb#-a#,  \verb#-j#, \verb#-c#, \verb#-s# and \verb#[job...]#
  command line options are specified, the comand resubmits \textbf{ALL} jobs that
  match either of the criteria (logical OR).

  For example, \verb#arcresub -s FAILED -c mycluster <jobid># will resubmit all failed
  jobs on the Grid, plus all jobs (in any state) on the cluster \verb#mycluster#, plus the job \verb#<jobid>#.
\end{framed}

@@

\begin{framed}
  When several of the \verb#-a#,  \verb#-j#, \verb#-c#, \verb#-s# and \verb#[job...]#
  command line options are specified, the comand migrates \textbf{ALL} jobs that
  match either of the criteria (logical OR).

  For example, \verb#arcmigrate -s FAILED -c mycluster <jobid># will migrate all failed
  jobs on the Grid, plus all jobs (in any state) on the cluster \verb#mycluster#, plus the job \verb#<jobid>#.
\end{framed}
